\onecolumn
\section {The Understudy}

The Understudy is a humanoid of rougly average height. They wear a harlequin costume consisting of red, orange, and black triangles. Due to their black gloves and tucked white socks, none of their skin is visible. They wear a dramatic mask that seems able to switch between various emotions, though never when someone is looking directly at them. Tricorn hat w/ feather.

\begin{monsterbox}{Ulysses Notorio Devida Emberto Ronaldo Sugartits Tyranno Umburto Debanthian Ymbyrto}
\begin{hangingpar}
\textit{Medium humanoid (ambigious), Level 7 Bard, Professional Understudy}
% Prof bonus +3
\end{hangingpar}
\dndline%
\basics[%
armorclass = 12,
% 20 from rolls
hitpoints = 35,
speed = {30 ft.}
]
\dndline%
\stats[%
% Rolls: 	12	13	12	14	13	13
% Lineage: +2 Char
% Lvl 4 feat: +2 Char
STR = \stat{12},
DEX = \stat{13},
CON = \stat{13},
INT = \stat{12},
WIS = \stat{13},
CHA = \stat{18}
]
\dndline%
\details[%
% Proficiencies: Performance, Persuasian, Deception, Acrobatics, History, Religion
% Expertise: Performance, Persuasion
skills={Performance +10, Persuasion +10, Deception +7, Acrobatics +4, History +4, Religion +4, All others +2},
damageimmunities={},
savingthrows={Dexterity +4, Charisma +7},
conditionimmunities={},
damageresistances={},
damagevulnerabilities={},
senses={passive Perception 12},
languages={Whatever the role requires},
challenge=3,
]
\dndline%

\monstersection{Actions}
  \DndMonsterAction{Spellcasting}
  The Understudy is a 2nd-level spellcaster. Its spellcasting ability is Charisma (spell save DC 12, +4 to hit with spell attacks). It has the following sorcerer spells prepared:
  \begin{DndMonsterSpells}
    \DndMonsterSpellLevel{Blade Ward, Minor Illusion, Vicious Mockery}
    \DndMonsterSpellLevel[1][4]{Bless, Charm Person, Guiding Bolt, Healing Word, Inflict Wounds}
    \DndMonsterSpellLevel[2][3]{Aid, Prayer of Healing*, Spiritual Weapon}
    \DndMonsterSpellLevel[3][3]{Beacon of Hope*, Mass Healing Word, Speak With Dead}
    \DndMonsterSpellLevel[4][1]{}
  \end{DndMonsterSpells}
  * Magical Discoveries
\DndMonsterAction{Bardic Inspiration} 4 uses, d8. Resets on a long rest. Can expend a spell slot to regain 1 use of Bardic Inspiration.
\DndMonsterAction{Rapier} +4 to hit. 1d8 + 1 piercing damage.

\monstersection{Reactions}
    \DndMonsterAction{Cutting Words} You learn to use your wit to supernaturally distract, confuse, and otherwise sap the confidence and competence of others. When a creature that you can see within 60 feet of yourself makes a damage roll or succeeds on an ability check or attack roll, you can take a Reaction to expend one use of your Bardic Inspiration; roll your Bardic Inspiration die, and subtract the number rolled from the creature's roll, reducing the damage or potentially turning the success into a failure.
    \DndMonsterAction{Countercharm} You can use musical notes or words of power to disrupt mind-influencing effects. If you or a creature within 30 feet of you fails a saving throw against an effect that applies the Charmed or Frightened condition, you can take a Reaction to cause the save to be rerolled, and the new roll has Advantage.

\monstersection{Equipment}
    \DndMonsterAction{Lute} Spellcasting focus
    \DndMonsterAction{Leather Armour} Spellcasting focus

\end{monsterbox}
