\onecolumn
\section{Credits}

\subsection{\LaTeX  templates}

%TODO: Put in latex template credits

\subsection {Map}
The battle map in this adventure was made using the following.

\textbf{Alon Mishne} for Mipui (mipui.net), the tool used to make the battle map

\subsection {Icons}

Several icons from game-icons.net (CC BY 3.0) are used in the map.

\textbf{Carl Olsen} for brutal-helm and spider-alt.

\textbf{Delapouite} for barrel, bookshelf, chest, overlord-helm, person, and secret-door.

\subsection {5e SRD}

This adventure (and the corresponding character sheets) use content from the 5e SRD (both version 5.1 and 5.2).

This work includes material taken from the System Reference Document 5.1 (“SRD 5.1”) by Wizards of
the Coast LLC and available at https://dnd.wizards.com/resources/systems-reference-document. The
SRD 5.1 is licensed under the Creative Commons Attribution 4.0 International License available at
https://creativecommons.org/licenses/by/4.0/legalcode

This work includes material from the System Reference Document 5.2.1 (“SRD 5.2.1”) by Wizards of the
Coast LLC, available at https://www.dndbeyond.com/srd. The SRD 5.2.1 is licensed under the Creative
Commons Attribution 4.0 International License, available at https://creativecommons.org/licenses/by/4.0/
legalcode.

\subsection {Special Thanks}

There's a lot of people who have helped me in my RPG adventures. I'd like to call out the following in particular

\textbf{Josh}, for running this adventure in Germany to a brand-new audience, and coming back with some excellent modifications

\textbf{Peter}, for introducing me to D\&D way back in 2008

\textbf{Richard}, for being the person who I have - by far - played the most TTRPGs with

You're always welcome at my table, lads.

