\begin{monsterbox}{Basitose Castle}
\monstersection{Lair Actions}

\begin{monsteraction}[Basitose Mists]
A 20-foot-radius sphere of fog centered on a point within range seeps into the room. The sphere spreads around corners, and its area is heavily obscured. It lasts for the duration or until a wind of moderate or greater speed (at least 10 miles per hour) disperses it.
\end{monsteraction}

\begin{monsteraction}[Collapse Roof]
A 20 foot cuddle of the roof collapses, dealing 2d8 bludgeoning damage to anyone caught in the cube. A DC 15 Dexterity saving throw halves the damage.
\end{monsteraction}

\begin{monsteraction}[Release The Weasels]
Once per day, if someone is standing next to the weasel release rope, they can use this lair action to pull the release rope, freeing the weasels in the canvas tied to the roof. 

This releases 30 weasels in six groups of 5 evenly around the waiting room.
\end{monsteraction}
\begin{monsteraction}[Root Cellar, Arise]
Grasping potato tendrils sprout from the ground in a 20-foot square starting form a point within range. For the duration, these smelly potatoes turn the ground in the area into difficult terrain.

A creature in the area when you cast the spell must succeed on a strength saving throw or be restrained by the awful, rotten potatoes until the spell ends. A creature restrained by the potatoes can use its action to make a DC13 Strength check against the tendrils. On a success, it frees itself.

When the spell ends, the potatoes melt into vodka.
\end{monsteraction}

\end{monsterbox}
